---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# projektROR

The goal of projektROR is to provide all necessary tools for data
analisys using logistic regression.

Our package supplies method for creating logistic regresion model. It
consists of all needed methods to help visualise dependencies between
variables. Let us compare two models with each other. Also with use of
AIC and BIC, for small data tables (a few variables), we can compare all
possible models. Our package also supplies method for K-Fold Cross
Validation. Using this package you can plot ROC curve and compute AUC,
too. One of its features is also possibility to compute and plot
predicted probabilities based on created model.

Package contains two exemplary data sets to get to know it better.

## Installation

You can install the development version of projektROR from
[GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ZuzannaNogala/projektROR", build_vignettes = TRUE)
```
## Data

First data set is `citrus`. This data set takes the color, weight, and
diameter of an “average” orange and grapefruit, which we can be used to
predict what type of fruit we have.

```{r citrus}
library(projektROR)
head(citrus)
```

Second one is a set of information about bank clients and status of
their loan payoff. Contains status of loan payoff from one month and
information such total income per year or education type, to use as
potential predictors in logistic regression.

```{r credit}
head(creditData)
```

## More Details

If you want learn more about package and see how all methods work look
at our html vignette.

```{r vigniette, eval = FALSE}
browseVignettes("projektROR")
```
